Quanta concentration and Transmission risk

### 2024-04-18 analysis/environmental-data.Rmd
Modeling fixes and visual updates
Update results presentation

```{r}
library(tidyverse)
library(lubridate)

@@

```{r}
co2_pl <- cont_df %>%
  mutate(time = floor_date(time, "10 minutes")) %>%
  group_by(mthdy, time, room) %>%
  summarize(co2 = mean(co2)) %>%
  ungroup() %>%
  mutate(room = factor(
    room,
    levels = c("Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = time, y = co2, color = mthdy)) +
  geom_step() +
  facet_wrap(~room) +
  coord_cartesian(expand = FALSE) +
  scale_x_datetime(date_breaks = "4 hours", date_labels = "%H:%M") +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(
    y = expression("CO"[2] * " (parts per million, ppm)"),
    title = "f"
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom",
    panel.spacing = unit(1, "lines"),
    legend.key.width = unit(0.275, "cm"),
    legend.key.height = unit(0.2, "cm")
  )

save_plot(
  co2_pl,
  pdf_file = "results/data/co2-levels-over-time.png",
  w = 10, h = 6
)
```

@@

aer_pl <- aer %>%
  mutate(room = factor(
    room,
    levels = c("Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = room, fill = room, y = aer)) +
  geom_boxplot() +
  # geom_jitter(
  #   mapping = aes(color = daytime),
  #   width = 0.2,
  #   height = 0,
  #   shape = 21
  # ) +
  scale_fill_manual(values = wes_palette("Royal2")[-1]) +
  scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, NA)) +
  labs(
    y = "Air changes per hour",
    title = "g"
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = c(0.8, 0.95)
  ) +
  guides(fill = "none")

save_plot(
  aer_pl,
  pdf_file = "results/data/air-changes-per-hour.png",
  w = 6, h = 6
)
```

>>>>

```{r}
library(tidyverse)
library(tidybayes)
library(lubridate)

@@

```{r}
co2_pl <- cont_df %>%
  mutate(time = floor_date(time, "10 minutes")) %>%
  group_by(mthdy, time, room) %>%
  summarize(co2 = mean(co2)) %>%
  ungroup() %>%
  mutate(room = factor(
    room,
    levels = c("Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = time, y = co2, color = mthdy)) +
  geom_step() +
  facet_wrap(~room) +
  coord_cartesian(expand = FALSE) +
  scale_x_datetime(date_breaks = "4 hours", date_labels = "%H:%M") +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(
    y = expression("CO"[2] * " (parts per million, ppm)")
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.key.width = unit(0.275, "cm"),
    legend.key.height = unit(0.2, "cm")
  )

save_plot(
  co2_pl,
  pdf_file = "results/data/co2-levels-over-time.png",
  w = 16, h = 10
)

cont_df %>%
  median_qi(co2, .width = .5) %>%
  mutate_if(is.numeric, round)
```

@@

aer_pl <- aer %>%
  mutate(room = factor(
    room,
    levels = c("Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = room, fill = room, y = aer)) +
  geom_boxplot() +
  # geom_jitter(
  #   mapping = aes(color = daytime),
  #   width = 0.2,
  #   height = 0,
  #   shape = 21
  # ) +
  scale_fill_manual(values = wes_palette("Royal2")[-1]) +
  scale_y_continuous(expand = expansion(mult = c(0, .05)), limits = c(0, NA)) +
  labs(
    y = "Air changes per hour",
    title = "d"
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = c(0.8, 0.95)
  ) +
  guides(fill = "none")

save_plot(
  aer_pl,
  pdf_file = "results/data/air-changes-per-hour.png",
  w = 8, h = 6
)
```

### 2024-04-18 analysis/patient-tracking.Rmd
Update results presentation

time_in_clin_pl <- time_in_clin %>%
  filter(tracking_end != "Possible HCW") %>%
  dplyr::select(-tracking_end) %>%
  melt(c("date", "patient_id")) %>%
  mutate(variable = factor(
    variable,
    levels = c("Clinic", "Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = variable, fill = variable, y = value)) +
  geom_boxplot() +
  scale_y_sqrt(breaks = c(0, 1, 10, 30, 60, 120, 180)) +
  scale_fill_manual(values = wes_palette("Royal2")) +
  labs(
    y = "Time in clinic (min)",
    title = "c"
  ) +
  theme_custom(8) +
  theme(
    legend.position = "none",
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title.position = "plot"
  )

save_plot(
  time_in_clin_pl,
  pdf_file = "results/data/time-in-clinic.png", w = 5.3, h = 6
)
```

@@

```{r}
clinic_occupancy <- df %>%
  group_by(date, time) %>%
  summarize(
    `Clinic` = n(),
    `Waiting room` = sum(is_waitingroom),
    `TB room` = sum(is_tbroom),
    `Corridor` = sum(is_passage)
  ) %>%
  ungroup() %>%
  melt(c("date", "time")) %>%
  mutate(
    variable = factor(
      variable,
      levels = c("Clinic", "Waiting room", "TB room", "Corridor")
    ),
    date = format(date, "%b %d"),
    date = factor(
      as.character(date),
      levels = c("Oct 13", "Oct 15", "Oct 25", "Nov 04", "Nov 05")
    ),
    time = as.POSIXct(format(time, format = "%H:%M:%S"), format = "%H:%M:%S")
  ) %>%
  filter(between(hour(time), 7, 16))

time_pl <- clinic_occupancy %>%
  filter(variable == "Clinic") %>%
  ggplot(aes(x = time, y = value, color = date)) +
  geom_step() +
  # ggh4x::facet_wrap2(~variable, axes = "x", remove_labels = "all") +
  coord_cartesian(expand = FALSE) +
  scale_x_datetime(date_breaks = "3 hours", date_labels = "%H:%M") +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(
    y = "Number of tracks",
    title = "b"
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.key.width = unit(0.275, "cm"),
    legend.key.height = unit(0.2, "cm")
  )

>>>>

time_in_clin_pl <- time_in_clin %>%
  filter(tracking_end != "Possible HCW") %>%
  dplyr::select(-tracking_end) %>%
  melt(c("date", "patient_id")) %>%
  filter(variable != "Clinic") %>%
  mutate(variable = factor(
    variable,
    levels = c("Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = variable, fill = variable, y = value)) +
  geom_boxplot() +
  scale_y_sqrt(breaks = c(0, 10, 30, 60, 120, 180)) +
  scale_fill_manual(values = wes_palette("Royal2")) +
  labs(
    y = "Time in clinic (min)",
    title = "c"
  ) +
  theme_custom(8) +
  theme(
    legend.position = "none",
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    plot.title.position = "plot"
  )

save_plot(
  time_in_clin_pl,
  pdf_file = "results/data/time-in-clinic.png", w = 8, h = 6
)
```

@@

```{r}
clinic_occupancy <- df %>%
  group_by(date, time) %>%
  summarize(
    `Clinic` = n(),
    `Waiting room` = sum(is_waitingroom),
    `TB room` = sum(is_tbroom),
    `Corridor` = sum(is_passage)
  ) %>%
  ungroup() %>%
  dplyr::select(-Clinic) %>%
  melt(c("date", "time")) %>%
  mutate(
    variable = factor(
      variable,
      levels = c("Clinic", "Waiting room", "TB room", "Corridor")
    ),
    date = format(date, "%b %d"),
    date = factor(
      as.character(date),
      levels = c("Oct 13", "Oct 15", "Oct 25", "Nov 04", "Nov 05")
    ),
    time = as.POSIXct(format(time, format = "%H:%M:%S"), format = "%H:%M:%S")
  ) %>%
  filter(between(hour(time), 7, 16))

time_pl <- clinic_occupancy %>%
  filter(variable != "Clinic") %>%
  group_by(time, variable) %>%
  summarise(
    mv = mean(value),
    sv = sd(value)
  ) %>%
  ungroup() %>%
  mutate(
    lv = mv - sv,
    uv = mv + sv
  ) %>%
  ggplot(aes(x = time)) +
  geom_line(
    aes(y = mv, color = variable)
  ) +
  geom_ribbon(
    aes(ymin = lv, ymax = uv, fill = variable),
    alpha = 0.4
  ) +
  # ggh4x::facet_wrap2(~variable, axes = "x", remove_labels = "all") +
  coord_cartesian(expand = FALSE) +
  scale_x_datetime(date_breaks = "3 hours", date_labels = "%H:%M") +
  scale_fill_manual(values = wes_palette("Royal2")) +
  scale_color_manual(values = wes_palette("Royal2")) +
  labs(
    y = "Number of tracks",
    title = "b"
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.key.width = unit(0.275, "cm"),
    legend.key.height = unit(0.2, "cm")
  )

### 2024-04-18 analysis/qctr.Rmd
Update results presentation

# plot
mean_quanta_pl <- plot_spatial(
  ggplot(mapping = aes(x = long, y = lat, group = group, fill = value)) +
    facet_wrap(~daytime) +
    geom_polygon(
      data = left_join(
        fortify(waiting_room),
        filter(main_mean_qc, room == "Waiting room"),
        by = c("id")
      )
    ) +
    geom_polygon(
      data = left_join(
        fortify(corridor),
        filter(main_mean_qc, room == "Corridor"),
        by = c("id")
      )
    ) +
    geom_polygon(
      data = left_join(fortify(tb_room),
        filter(main_mean_qc, room == "TB room"),
        by = c("id")
      )
    ) +
    labs(
      fill = expression("Mean quanta concentration (quanta m"^-3 * " " * "x 10e"^-3 * ")"),
      title = "a"
    ) +
    scale_fill_gradientn(
      colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"),
      labels = function(x) round(1e3 * x / (0.25^2 * 3), 1)
    ),
  8
) +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.key.height = unit(0.2, "cm"),
    legend.key.width = unit(1.5, "cm"),
    legend.title = element_text(margin = margin(r = 10))
  )

mean_quanta_pl
```

@@

```{r}
average_trans_risk <- function(file) {
  average_tr <- read.table(file) %>%
    set_names(c("sim", "patient_id", "P")) %>%
    mutate(
      mthdy = stringi::stri_extract(file, regex = "\\d{2}-\\d{2}"),
      patient_id = paste(mthdy, patient_id, sep = "-")
    ) %>%
    group_by(patient_id) %>%
    summarize(
      P_mean = mean(P),
      P025 = quantile(P, .025),
      P975 = quantile(P, .975),
      P25 = quantile(P, .25),
      P75 = quantile(P, .75),
      P20 = quantile(P, .2),
      P80 = quantile(P, .8)
    ) %>%
    ungroup() %>%
    left_join(track %>%
      mutate(
        mth = lubridate::month(time),
        dy = lubridate::day(time)
      ) %>%
      group_by(patient_id, mth, dy) %>%
      slice(1) %>%
      ungroup() %>%
      mutate(dy = ifelse(nchar(dy) == 1, paste0("0", dy), dy)) %>%
      mutate(patient_id = paste(
        mth, dy,
        patient_id,
        sep = "-"
      )) %>%
      dplyr::select(patient_id, tracking_end)) %>%
    filter(tracking_end != "Possible HCW") %>%
    dplyr::select(-tracking_end) %>%
    mutate(
      P_col = ifelse(P_mean < .001, "Low",
        ifelse(P_mean < .01, "Medium", "High")
      ),
      P_col = factor(P_col, levels = c("Low", "Medium", "High")),
      P_ann = 1 - (1 - P_mean)^12
    )
  return(average_tr)
}

@@

main_tr <- main_tr %>% unnest(value)

main_tr %>%
  group_by(P_col) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(prop = round(n / sum(n) * 100, 0))

# annotation
annotate_average_trans_risk <- function(tr) {
  roi_annon <- tr %>%
    summarize(
      mean_P = mean(P_mean),
      lower_P = quantile(P_mean, .025),
      upper_P = quantile(P_mean, .975),
      mean_P_ann = mean(P_ann),
      lower_P_ann = quantile(P_ann, .025),
      upper_P_ann = quantile(P_ann, .975)
    ) %>%
    mutate(
      across(c(mean_P, lower_P, upper_P), ~ round_k(100 * .x, 3)),
      lab = paste0(
        mean_P, "%",
        " (95%-CrI ", lower_P, "% – ", upper_P, "%)"
      ),
      across(c(mean_P_ann, lower_P_ann, upper_P_ann), ~ round_k(100 * .x, 2)),
      lab_ann = paste0(
        mean_P_ann, "%",
        " (95%-CrI ", lower_P_ann, "% – ", upper_P_ann, "%)"
      )
    )
  return(roi_annon)
}

@@

main_annon$lab
main_annon$lab_ann

# plot
roi_pl <- ggplot(
  data = main_tr,
  mapping = aes(x = P_mean)
) +
  geom_histogram(
    mapping = aes(fill = P_col),
    binwidth = .0005,
    boundary = 1
  ) +
  geom_text(
    data = main_annon,
    mapping = aes(x = Inf, y = Inf, label = lab),
    size = 8 / cm(1),
    hjust = 1, vjust = 2
  ) +
  scale_fill_manual(values = wes_palette("Darjeeling1")[c(2, 3, 1)]) +
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(
    labels = function(x) x * 100,
    breaks = c(0, 0.001, 0.005, 0.01, 0.015, 0.02),
    limits = c(0, 0.02)
  ) +
  scale_y_sqrt(
    labels = scales::comma,
    breaks = c(0, 25, 100, 250, 500, 1000)
  ) +
  labs(
    x = "Risk of infection (%)",
    y = "Number of people",
    title = "b"
  ) +
  theme_custom() +
  theme(
    legend.position = c(0.7, .3),
    legend.title = element_blank(),
    legend.key.height = unit(.3, "cm"),
    legend.key.width = unit(.2, "cm"),
    legend.direction = "horizontal",
    panel.spacing = unit(2, "cm")
  )

roi_pl
```

```{r}
main_tr <- main_tr %>%
  mutate(P_unc = P75 - P25)

@@

main_focus_pl <- main_tr %>%
  ggplot(aes(x = P_unc, y = P_mean)) +
  geom_point(shape = 4) +
  annotate(
    "point",
    x = hr_lu_pt$P_unc,
    y = hr_lu_pt$P_mean,
    size = 7,
    shape = 1,
    color = "red"
  ) +
  annotate(
    geom = "segment",
    x = hr_lu_pt$P_unc + .00002,
    y = hr_lu_pt$P_mean + .0004,
    xend = hr_lu_pt$P_unc + .00008,
    yend = hr_lu_pt$P_mean + .004,
    arrow = arrow(length = unit(0.1, "cm")),
    color = "red"
  ) +
  annotate(
    geom = "text",
    x = hr_lu_pt$P_unc + .00008,
    y = hr_lu_pt$P_mean + .004,
    label = "Moderate risk,\nlow uncertainty",
    hjust = -.1,
    size = 6.5 / cm(1),
    color = "red"
  ) +
  scale_y_continuous(
    expand = expansion(mult = c(0.01, 0.01)),
    limits = c(0, .01),
    breaks = seq(0, .01, .0025),
    labels = function(x) round_k(100 * x, 3)
  ) +
  scale_x_continuous(
    expand = expansion(mult = c(0.01, 0.01)),
    limits = c(0, .002),
    breaks = seq(0, .002, .0005),
    labels = function(x) round_k(100 * x, 3)
  ) +
  labs(
    x = "Uncertainty (interquartile range, pp)",
    y = "Mean risk of infection (%)",
    title = "c"
  ) +
  theme_bw2() +
  theme(
    plot.title.position = "plot",
    plot.title = element_text(size = 10, face = 2),
  )

main_focus_pl
```

@@

@@

amod_est %>%
  group_by(variable) %>%
  summarize(
    lower = quantile(value, .025),
    mean = mean(value),
    upper = quantile(value, .975)
  ) %>%
  mutate(across(c(lower, mean, upper), ~ round_k(.x, 2)))

amod_est_pl <- ggplot(amod_est, aes(y = variable, x = value)) +
  geom_vline(aes(xintercept = 1), linetype = "dotted", color = "red") +
  stat_interval(point_interval = "mean_qi") +
  stat_summary(
    geom = "point",
    fun = mean,
    size = 2,
    shape = 21,
    fill = "white"
  ) +
  labs(
    x = "Odds ratio of the modeled risk of infection for a doubling in the predictor",
    title = "d",
    color = "CrI"
  ) +
  scale_y_discrete(
    labels = c(
      # "Air change rate",
      "Time in clinic",
      "No. close contacts",
      "Time close contact"
    )
  ) +
  scale_color_brewer(
    labels = paste0(c(95, 80, 50), "%")
  ) +
  theme_custom() +
  theme(
    axis.title.y = element_blank(),
    legend.position = "right",
    legend.key.size = unit(.3, "cm")
  )

amod_est_pl
```

```{r main-figure}
main_fig <- grid.arrange(
  mean_quanta_pl,
  grid.arrange(roi_pl, main_focus_pl, ncol = 2),
  amod_est_pl,
  ncol = 1,
  heights = c(10, 6, 4)
)

ggsave(
  main_fig,
  filename = "results/modeling/main-figure.png",
  width = 16 / cm(1),
  height = 16 / cm(1)
)
```

@@

## Additional analyses

```{r additional-analyses}
# files
files_nm <- list.files("simulations/nomasks/",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_vent <- list.files("simulations/vent/",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_prev <- list.files("simulations/prevalence/",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_susp <- list.files("simulations/suspected/",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)

# average risk
nm_tr <- map_dfr(files_nm, average_trans_risk)
vent_tr <- map_dfr(files_vent, average_trans_risk)
prev_tr <- map_dfr(files_prev, average_trans_risk)
susp_tr <- map_dfr(files_susp, average_trans_risk)

@@

susp_tr %>%
  group_by(P_col) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(prop = round(n / sum(n) * 100, 0))

main_tr %>%
  dplyr::select(patient_id, P_mean) %>%
  rename(`Spatiotemporal model` = P_mean) %>%
  left_join(
    nm_tr %>%
      dplyr::select(patient_id, P_mean) %>%
      rename(`No mask wearing` = P_mean)
  ) %>%
  left_join(
    vent_tr %>%
      dplyr::select(patient_id, P_mean) %>%
      rename(`Lower ventilation` = P_mean)
  ) %>%
  mutate(
    mask_factor = `No mask wearing` / `Spatiotemporal model`,
    vent_factor = `Lower ventilation` / `Spatiotemporal model`
  ) %>%
  mean_qi(mask_factor, vent_factor) %>%
  gather() %>%
  head(6) %>%
  mutate(value = round(as.numeric(value), 2))

# combine
tr_comp <- rbind(
  nm_tr %>% mutate(scenario = "No mask wearing"),
  vent_tr %>% mutate(scenario = "Lower ventilation"),
  prev_tr %>% mutate(scenario = "Prevalence-based model"),
  susp_tr %>% mutate(scenario = "Suspected-based model")
) %>%
  mutate(
    scenario = factor(scenario, levels = c(
      "Spatiotemporal model",
      "Temporal model",
      "No mask wearing",
      "Lower ventilation",
      "Prevalence-based model",
      "Suspected-based model"
    ))
  )

# annotation
nm_annon <- annotate_average_trans_risk(nm_tr)
vent_annon <- annotate_average_trans_risk(vent_tr)
prev_annon <- annotate_average_trans_risk(prev_tr)
susp_annon <- annotate_average_trans_risk(susp_tr)

annon_comp <- rbind(
  nm_annon %>% mutate(scenario = "No mask wearing"),
  vent_annon %>% mutate(scenario = "Lower ventilation"),
  prev_annon %>% mutate(scenario = "Prevalence-based model"),
  susp_annon %>% mutate(scenario = "Suspected-based model")
) %>%
  mutate(
    scenario = factor(scenario, levels = c(
      "No mask wearing",
      "Lower ventilation",
      "Suspected-based model",
      "Prevalence-based model"
    ))
  )

# plot mean
mean_roi_comp_pl <- ggplot(
  tr_comp,
  aes(x = P_mean)
) +
  geom_histogram(
    mapping = aes(fill = P_col),
    binwidth = .0005,
    boundary = 1
  ) +
  geom_text(
    data = annon_comp,
    mapping = aes(x = Inf, y = Inf, label = lab),
    size = 8 / cm(1),
    hjust = 1, vjust = 2
  ) +
  facet_wrap(~scenario, ncol = 2) +
  scale_fill_manual(values = wes_palette("Darjeeling1")[c(2, 3, 1)]) +
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(
    labels = function(x) x * 100,
    breaks = c(0, 0.001, 0.005, 0.01, 0.015, 0.02),
    limits = c(0, 0.02)
  ) +
  scale_y_sqrt(
    labels = scales::comma,
    breaks = c(0, 25, 100, 250, 500, 1000),
    limits = c(0, 1000)
  ) +
  labs(
    x = "Risk of infection (%)",
    y = "Number of clinical attendees"
  ) +
  theme_custom() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.key.height = unit(.6, "cm"),
    legend.key.width = unit(.4, "cm"),
    panel.spacing = unit(2, "cm")
  )

@@

>>>>

# plot
mean_quanta_pl <- plot_spatial(
  ggplot(mapping = aes(x = long, y = lat, group = group, fill = value)) +
    facet_wrap(~daytime) +
    geom_polygon(
      data = left_join(
        fortify(waiting_room),
        filter(main_mean_qc, room == "Waiting room"),
        by = c("id")
      )
    ) +
    geom_polygon(
      data = left_join(
        fortify(corridor),
        filter(main_mean_qc, room == "Corridor"),
        by = c("id")
      )
    ) +
    geom_polygon(
      data = left_join(fortify(tb_room),
        filter(main_mean_qc, room == "TB room"),
        by = c("id")
      )
    ) +
    labs(
      fill = expression("Mean quanta concentration (quanta m"^-3 * " " * "x 10e"^-3 * ")")
    ) +
    scale_fill_gradientn(
      colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"),
      labels = function(x) round(1e3 * x / (0.25^2 * 3), 1)
    ),
  8
) +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.key.height = unit(0.2, "cm"),
    legend.key.width = unit(1.5, "cm"),
    legend.title = element_text(margin = margin(r = 10))
  )

save_plot(
  mean_quanta_pl,
  "results/modeling/mean-quanta-concentration.png",
  w = 16,
  h = 8
)
```

@@

```{r}
average_trans_risk <- function(file) {
  average_tr <- read.table(file) %>%
    set_names(c("sim", "patient_id", "P")) %>%
    mutate(
      mthdy = stringi::stri_extract(file, regex = "\\d{2}-\\d{2}"),
      patient_id = paste(mthdy, patient_id, sep = "-")
    ) %>%
    group_by(patient_id) %>%
    summarize(
      P_mean = mean(P),
      P025 = quantile(P, .025),
      P975 = quantile(P, .975),
      P25 = quantile(P, .25),
      P75 = quantile(P, .75),
      P20 = quantile(P, .2),
      P80 = quantile(P, .8)
    ) %>%
    ungroup() %>%
    left_join(track %>%
      mutate(
        mth = lubridate::month(time),
        dy = lubridate::day(time)
      ) %>%
      group_by(patient_id, mth, dy) %>%
      slice(1) %>%
      ungroup() %>%
      mutate(dy = ifelse(nchar(dy) == 1, paste0("0", dy), dy)) %>%
      mutate(patient_id = paste(
        mth, dy,
        patient_id,
        sep = "-"
      )) %>%
      dplyr::select(patient_id, tracking_end)) %>%
    filter(tracking_end != "Possible HCW") %>%
    dplyr::select(-tracking_end) %>%
    mutate(
      P_col = ifelse(P_mean < .001, "Low",
        ifelse(P_mean < .01, "Medium", "High")
      ),
      P_col = factor(P_col, levels = c("Low", "Medium", "High"))
    )
  return(average_tr)
}

@@

main_tr <- main_tr %>%
  unnest(value) %>%
  dplyr::select(-files)

# annotation
annotate_average_trans_risk <- function(tr) {
  roi_annon <- tr %>%
    summarize(
      mean_P = mean(P_mean),
      lower_P = quantile(P_mean, .2),
      upper_P = quantile(P_mean, .8)
    ) %>%
    mutate(
      across(c(mean_P, lower_P, upper_P), ~ round_k(100 * .x, 2)),
      lab = paste0(
        mean_P, "%",
        " (80%-CrI ", lower_P, "% – ", upper_P, "%)"
      )
    )
  return(roi_annon)
}

@@

main_annon
```

```{r}
main_tr <- main_tr %>%
  mutate(P_unc = P80 - P20)

@@

main_focus_pl <- main_tr %>%
  ggplot(aes(x = P_unc, y = P_mean)) +
  geom_point(shape = 4) +
  annotate(
    "point",
    x = hr_lu_pt$P_unc,
    y = hr_lu_pt$P_mean,
    size = 7,
    shape = 1,
    color = "red"
  ) +
  annotate(
    geom = "segment",
    x = hr_lu_pt$P_unc + .00002,
    y = hr_lu_pt$P_mean + .0004,
    xend = hr_lu_pt$P_unc + .00008,
    yend = hr_lu_pt$P_mean + .004,
    arrow = arrow(length = unit(0.1, "cm")),
    color = "red"
  ) +
  annotate(
    geom = "text",
    x = hr_lu_pt$P_unc + .00008,
    y = hr_lu_pt$P_mean + .004,
    label = "Moderate risk,\nlow uncertainty",
    hjust = -.1,
    size = 6.5 / cm(1),
    color = "red"
  ) +
  scale_y_continuous(
    expand = expansion(mult = c(0.01, 0.01)),
    limits = c(0, .01),
    breaks = seq(0, .01, .0025),
    labels = function(x) round_k(100 * x, 3)
  ) +
  scale_x_continuous(
    expand = expansion(mult = c(0.01, 0.01)),
    limits = c(0, .002),
    breaks = seq(0, .002, .0005),
    labels = function(x) round_k(100 * x, 3)
  ) +
  labs(
    x = "Uncertainty (80%-CrI, pp)",
    y = "Mean risk of infection (%)"
  ) +
  theme_bw2() +
  theme(
    plot.title.position = "plot",
    plot.title = element_text(size = 10, face = 2),
    plot.margin = margin(.5, .5, .5, .5, "cm")
  )

save_plot(
  main_focus_pl,
  "results/modeling/patient-risk-focus-plot.png",
  w = 12,
  h = 10
)
```

@@

# risk per hour in clinic
assoc_df %>%
  filter(tracking_end != "Possible HCW") %>%
  mutate(
    rph = 60 * P_mean / time_in_clinic,
    rpy = 1 - (1 - rph)^12
  ) %>%
  mean_qi(rph, rpy, .width = .8, na.rm = TRUE) %>%
  mutate_if(is.numeric, ~ round_k(100 * .x, 2)) %>%
  unlist()

@@

amod_est %>%
  group_by(variable) %>%
  summarize(
    lower = quantile(value, .025),
    mean = mean(value),
    upper = quantile(value, .975)
  ) %>%
  mutate(across(c(lower, mean, upper), ~ round_k(.x, 2)))
```

@@

## IPC comparison

```{r additional-analyses}
# files
files_nm <- list.files("simulations/nomasks/",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_vent <- list.files("simulations/vent/",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_nmvent <- list.files("simulations/nomasksvent/",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)

# average risk
nm_tr <- map_dfr(files_nm, average_trans_risk)
vent_tr <- map_dfr(files_vent, average_trans_risk)
nmvent_tr <- map_dfr(files_nmvent, average_trans_risk)

@@

nmvent_tr %>%
  group_by(P_col) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(prop = round(n / sum(n) * 100, 0))

main_tr %>%
  dplyr::select(patient_id, P_mean) %>%
  rename(`Spatiotemporal model` = P_mean) %>%
  left_join(
    nm_tr %>%
      dplyr::select(patient_id, P_mean) %>%
      rename(`No mask wearing` = P_mean)
  ) %>%
  left_join(
    vent_tr %>%
      dplyr::select(patient_id, P_mean) %>%
      rename(`Lower ventilation` = P_mean)
  ) %>%
  left_join(
    nmvent_tr %>%
      dplyr::select(patient_id, P_mean) %>%
      rename(`No mask wearing and lower ventilation` = P_mean)
  ) %>%
  mutate(
    mask_factor = `No mask wearing` / `Spatiotemporal model`,
    vent_factor = `Lower ventilation` / `Spatiotemporal model`,
    nmvent_factor = `No mask wearing and lower ventilation` / `Spatiotemporal model`
  ) %>%
  mean_qi(mask_factor, vent_factor, nmvent_factor) %>%
  gather() %>%
  head(9) %>%
  mutate(value = round(as.numeric(value), 1))

# combine
tr_comp <- rbind(
  main_tr %>% mutate(scenario = "a   Mask use and high ventilation"),
  nm_tr %>% mutate(scenario = "b   No mask use and high ventilation"),
  vent_tr %>% mutate(scenario = "c   Mask use and normal ventilation"),
  nmvent_tr %>% mutate(scenario = "d   No mask use and normal ventilation")
) %>%
  mutate(scenario = factor(scenario, levels = unique(scenario)))

# annotation
nm_annon <- annotate_average_trans_risk(nm_tr)
vent_annon <- annotate_average_trans_risk(vent_tr)
nmvent_annon <- annotate_average_trans_risk(nmvent_tr)

annon_comp <- rbind(
  main_annon %>% mutate(scenario = "a   Mask use and high ventilation"),
  nm_annon %>% mutate(scenario = "b   No mask use and high ventilation"),
  vent_annon %>% mutate(scenario = "c   Mask use and normal ventilation"),
  nmvent_annon %>% mutate(scenario = "d   No mask use and normal ventilation")
) %>%
  mutate(scenario = factor(scenario, levels = unique(scenario)))

# plot mean
mean_roi_comp_pl <- ggplot(
  tr_comp,
  aes(x = P_mean)
) +
  geom_histogram(
    mapping = aes(fill = P_col),
    binwidth = .0005,
    boundary = 1
  ) +
  geom_text(
    data = annon_comp,
    mapping = aes(x = Inf, y = Inf, label = lab),
    size = 8 / cm(1),
    hjust = 1, vjust = 2
  ) +
  facet_wrap(~scenario, ncol = 2) +
  scale_fill_manual(values = wes_palette("Darjeeling1")[c(2, 3, 1)]) +
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(
    labels = function(x) x * 100,
    breaks = c(0, 0.001, 0.005, 0.01, 0.015, 0.02),
    limits = c(0, 0.02)
  ) +
  scale_y_sqrt(
    labels = scales::comma,
    breaks = c(0, 25, 100, 250, 500, 1000),
    limits = c(0, NA)
  ) +
  labs(
    x = "Risk of infection (%)",
    y = "Number of clinical attendees"
  ) +
  theme_custom() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.key.height = unit(.6, "cm"),
    legend.key.width = unit(.4, "cm"),
    panel.spacing = unit(2, "cm"),
    strip.text = element_text(hjust = 0)
  )

@@

## Additional analysis

```{r} 
files_prev <- list.files("simulations/prevalence/",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_susp <- list.files("simulations/suspected/",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)

prev_tr <- map_dfr(files_prev, average_trans_risk)
susp_tr <- map_dfr(files_susp, average_trans_risk)

tr_assum <- rbind(
  prev_tr %>% mutate(scenario = "a   Prevalence-based model"),
  susp_tr %>% mutate(scenario = "b   Suspected-based model")
) %>%
  mutate(scenario = factor(scenario, levels = unique(scenario)))

prev_annon <- annotate_average_trans_risk(prev_tr)
susp_annon <- annotate_average_trans_risk(susp_tr)

annon_assum <- rbind(
  prev_annon %>% mutate(scenario = "a   Prevalence-based model"),
  susp_annon %>% mutate(scenario = "b   Suspected-based model")
) %>%
  mutate(scenario = factor(scenario, levels = unique(scenario)))

# plot mean
mean_roi_assum_pl <- ggplot(
  tr_assum,
  aes(x = P_mean)
) +
  geom_histogram(
    mapping = aes(fill = P_col),
    binwidth = .0005,
    boundary = 1
  ) +
  geom_text(
    data = annon_assum,
    mapping = aes(x = Inf, y = Inf, label = lab),
    size = 8 / cm(1),
    hjust = 1, vjust = 2
  ) +
  facet_wrap(~scenario, ncol = 2) +
  scale_fill_manual(values = wes_palette("Darjeeling1")[c(2, 3, 1)]) +
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(
    labels = function(x) x * 100,
    breaks = c(0, 0.001, 0.005, 0.01, 0.015, 0.02),
    limits = c(0, 0.02)
  ) +
  scale_y_sqrt(
    labels = scales::comma,
    breaks = c(0, 25, 100, 250, 500, 1000),
    limits = c(0, NA)
  ) +
  labs(
    x = "Risk of infection (%)",
    y = "Number of clinical attendees"
  ) +
  theme_custom() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.key.height = unit(.6, "cm"),
    legend.key.width = unit(.4, "cm"),
    panel.spacing = unit(2, "cm"),
    strip.text = element_text(hjust = 0)
  )

save_plot(
  mean_roi_assum_pl,
  "results/modeling/mean-roi-assumptions.png",
  w = 16,
  h = 7
)
```
